Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-07 paper.tex
minor changes

\textbf{(RP6)} develop automated synthesis approaches that are algorithmically and numerically sound, in order to handle control software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.

>>>>

\textbf{(RP6)} develop automated synthesis approaches that are algorithmically and numerically sound, in order to handle (control) software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.
